Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and neurodevelopment: A study based on the parametric g-formula

### 2024-01-02 output/paper/_si.qmd
First round of modifications for tables and figures done.

::: {#supptbl-codebook-1}
```{r codebook-1}
codebook_1
```
Codebook for the covariates used in the estimation of the marginal comparisons of \acr{edcs} on \acr{hitrtse}.
:::

::: {#supptbl-codebook-2}
```{r codebook-2}
codebook_2
```
Codebook for the covariates used in the estimation of the marginal comparisons of \acr{edcs} on the glucocorticosteroids.
:::

::: {#supptbl-codebook-3}
```{r codebook-3}
codebook_3
```
Codebook for the covariates used in the estimation of the marginal comparisons of the glucocorticosteroids on \acr{hitrtse}.
:::

@@

::: {#supptbl-info-chems}
```{r info-chems}
edcs_info <- myphd::edcs_information() |>
  tidylog::select(-c(chem_id, smiles, ctd_id, exposome_explorer_id)) |>
  tidylog::mutate(
    var = janitor::make_clean_names(
      short_name,
      replace = c(`-` = ""),
      case = "none"
    ) |>
      tolower()
  ) |>
  tidylog::relocate(var, .after = short_name)
gt::gt(edcs_info,
       groupname_col = "class") |>
  gt::sub_values(
    values = c("NA"),
    replacement = ""
  ) |>
  gt::cols_label(
    full_name = "Compound",
    short_name = "Symbol",
    var = "Variable name",
    pubchem_cid = "PubChem CID",
    parental_compound = "Parental compound"
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```
Information about non-persistent EDCs, including the full compound name, the standard symbol, the used variable name, the identifier from PubChem, and the parental compound.
:::

@@

::: {#supptbl-info-mets}
```{r info-mets}
mets_info <- readODS::read_ods(
  path = here::here("docs", "steroids.ods")
) |>
  tidylog::select(analyte, acronym, type, hmdb_id, cas_number)
gt::gt(mets_info,
       groupname_col = "type") |>
  gt::sub_values(
    values = c("NA"),
    replacement = ""
  ) |>
  gt::cols_label(
    analyte = "Metabolite",
    acronym = "Symbol",
    hmdb_id = "HMDB ID",
    cas_number = "CAS number"
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  ) |>
  gt::tab_footnote(
    footnote = "Abbreviations: Human Metabolome Database (HMDB); Chemical Abstracts Service (CAS).",
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
Information about the glucocorticosteroids, including the full metabolite name, the standard symbol, the identifier from the HMDB, and the CAS number.
:::

::: {#supptbl-lloq-mets}
```{r lloq-mets}
lloq_mets <- load_steroids()$loq |>
  tidylog::mutate(
    Metabolite = stringr::str_replace(
      metabolite,
      "^X", ""
    )
  ) |>
  tidylog::rename(
    LLOQ = "loq"
  ) |>
  tidylog::select(-metabolite)
gt::gt(lloq_mets |> dplyr::arrange(Metabolite)) |>
  gt::tab_footnote(
    footnote = "Abbreviations: lower limit of quantification (LLOQ), expressed in nanograms per millilitre."
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
Lower limits of quantification for the glucocorticosteroids.
:::

@@

::: {#supptbl-balance-1}
```{r balance-1}
balance_1 |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
Effective sample size before and after balancing weights estimation (exposures: \acr{edcs}; outcome: \acr{hitrtse}).
:::

::: {#supptbl-balance-2}
```{r balance-2}
balance_2 |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
Effective sample size before and after balancing weights estimation (exposures: \acr{edcs}; outcomes: glucocorticosteroids).
:::

::: {#supptbl-balance-3}
```{r balance-3}
balance_3 |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  gt::gt() |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
Effective sample size before and after balancing weights estimation (exposures: glucocorticosteroids; outcome: \acr{hitrtse}).
:::

@@

::: {#supptbl-weights-1}
```{r weights-1}
tidy_res_weighted_fits(
  dat_tbl = weights_1$dat_tbl,
  dat_plt = weights_1$dat_plt,
  sa_var = NULL
)$table
```
Summary statistics of the estimated balancing weights (exposures: \acr{edcs}; outcome: \acr{hitrtse}).
:::

::: {#supptbl-weights-2}
```{r weights-2}
tidy_res_weighted_fits(
  dat_tbl = weights_2$dat_tbl,
  dat_plt = weights_2$dat_plt,
  sa_var = NULL
)$table
```
Summary statistics of the estimated balancing weights (exposures: \acr{edcs}; outcomes: glucocorticosteroids).
:::

::: {#supptbl-weights-3}
```{r weights-3}
tidy_res_weighted_fits(
  dat_tbl = weights_3$dat_tbl,
  dat_plt = weights_3$dat_plt,
  sa_var = NULL
)$table
```
Summary statistics of the estimated balancing weights (exposures: glucocorticosteroids; outcome: \acr{hitrtse}).
:::

@@

::: {#supptbl-weights-1sa}
```{r weights-1sa}
tidy_res_weighted_fits(
  dat_tbl = weights_1SA$dat_tbl,
  dat_plt = weights_1SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
Summary statistics of the estimated balancing weights for effect modification (exposures: \acr{edcs}; outcome: \acr{hitrtse}; modifier: sex).
:::

::: {#supptbl-weights-2sa}
```{r weights-2sa}
tidy_res_weighted_fits(
  dat_tbl = weights_2SA$dat_tbl,
  dat_plt = weights_2SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
Summary statistics of the estimated balancing weights for effect modification (exposures: \acr{edcs}; outcomes: glucocorticosteroids; modifier: sex).
:::

::: {#supptbl-weights-3sa}
```{r weights-3sa}
tidy_res_weighted_fits(
  dat_tbl = weights_3SA$dat_tbl,
  dat_plt = weights_3SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
Summary statistics of the estimated balancing weights for effect modification (exposures: glucocorticosteroids; outcome: \acr{hitrtse}; modifier: sex).
:::

@@

viz_desc_vars(
  dat = load_dat_request()$dat,
  vars = vars_of_interest(append_to_chem = "cdesc")$chemicals,
  fct_levels = c(1, 2, 3, 4),
  is_chem = TRUE
)$plot
```
**Measurement classification of \acr{edcs}, by cohort.**
Coding: 1, quantifiable; 2, <LOD; 3, interference or out of range; 4. not analysed.
:::

@@

viz_desc_vars(
  dat = myphd::extract_cohort(load_steroids()$desc,
                              id_var = id_var,
                              st = 1, en = 3) |>
    tidylog::mutate(
      cohort = dplyr::case_when(
        cohort == "EDE" ~ "EDEN",
        cohort == "KAN" ~ "KANC",
        cohort == "MOB" ~ "MOBA",
        cohort == "RHE" ~ "RHEA",
        .default = cohort
      )
    ),
  vars = vars_of_interest(append_to_chem = NULL)$metabolites |>
    paste0("_cdesc"),
  fct_levels = c(1, 2, 3, 4),
  is_chem = FALSE
)$plot
```
**Measurement classification of the glucocorticosteroids, by cohort.**
Coding: 1, quantifiable; 2, <LOQ; 3, interference or out of range; 4, not detected.
:::

>>>>

::: {#supptbl-codebook-1}
```{r codebook-1}
codebook_1
```
**Codebook for the covariates used in the estimation of the marginal comparisons of \acr{edcs} on \acr{hitrtse}.**
:::

::: {#supptbl-codebook-2}
```{r codebook-2}
codebook_2
```
**Codebook for the covariates used in the estimation of the marginal comparisons of \acr{edcs} on the glucocorticosteroids.**
:::

::: {#supptbl-codebook-3}
```{r codebook-3}
codebook_3
```
**Codebook for the covariates used in the estimation of the marginal comparisons of the glucocorticosteroids on \acr{hitrtse}.**
:::

@@

::: {#supptbl-info-chems}
```{r info-chems}
edcs_info <- myphd::edcs_information() |>
  tidylog::select(-c(chem_id, smiles, ctd_id, exposome_explorer_id)) |>
  tidylog::mutate(
    var = janitor::make_clean_names(
      short_name,
      replace = c(`-` = ""),
      case = "none"
    ) |>
      tolower()
  ) |>
  tidylog::relocate(var, .after = short_name)
gt::gt(edcs_info,
       groupname_col = "class") |>
  gt::sub_values(
    values = c("NA"),
    replacement = ""
  ) |>
  gt::cols_label(
    full_name = "Compound",
    short_name = "Symbol",
    var = "Variable name",
    pubchem_cid = "PubChem CID",
    parental_compound = "Parental compound"
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```
**Information about non-persistent EDCs, including the full compound name, the standard symbol, the used variable name, the identifier from PubChem, and the parental compound.**
:::

@@

::: {#supptbl-info-mets}
```{r info-mets}
mets_info <- readODS::read_ods(
  path = here::here("docs", "steroids.ods")
) |>
  tidylog::select(analyte, acronym, type, hmdb_id, cas_number)
gt::gt(mets_info,
       groupname_col = "type") |>
  gt::sub_values(
    values = c("NA"),
    replacement = ""
  ) |>
  gt::cols_label(
    analyte = "Metabolite",
    acronym = "Symbol",
    hmdb_id = "HMDB ID",
    cas_number = "CAS number"
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  ) |>
  gt::tab_footnote(
    footnote = "Abbreviations: Human Metabolome Database (HMDB); Chemical Abstracts Service (CAS).",
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
**Information about the glucocorticosteroids, including the full metabolite name, the standard symbol, the identifier from the HMDB, and the CAS number.**
:::

::: {#supptbl-lloq-mets}
```{r lloq-mets}
lloq_mets <- load_steroids()$loq |>
  tidylog::mutate(
    Metabolite = stringr::str_replace(
      metabolite,
      "^X", ""
    )
  ) |>
  tidylog::rename(
    LLOQ = "loq"
  ) |>
  tidylog::select(-metabolite, Metabolite, LLOQ)
gt::gt(lloq_mets |> dplyr::arrange(Metabolite)) |>
  gt::tab_footnote(
    footnote = "Abbreviations: lower limit of quantification (LLOQ), expressed in nanograms per millilitre."
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
**Lower limits of quantification for the glucocorticosteroids (HELIX Study; 2013-2016).**
:::

@@

::: {#supptbl-balance-1}
```{r balance-1}
balance_1 |>
  tidylog::rename(Exposure = "exposure") |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  )
```
**Effective sample size before and after balancing weights estimation (exposures: \acr{edcs}; outcome: \acr{hitrtse}) (HELIX Study; 2013-2016).**
:::

::: {#supptbl-balance-2}
```{r balance-2}
balance_2 |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  )
```
**Effective sample size before and after balancing weights estimation (exposures: \acr{edcs}; outcomes: glucocorticosteroids) (HELIX Study; 2013-2016).**
:::

::: {#supptbl-balance-3}
```{r balance-3}
balance_3 |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  gt::gt() |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  )
```
**Effective sample size before and after balancing weights estimation (exposures: glucocorticosteroids; outcome: \acr{hitrtse}) (HELIX Study; 2013-2016).**
:::

@@

::: {#supptbl-weights-1}
```{r weights-1}
tidy_res_weighted_fits(
  dat_tbl = weights_1$dat_tbl,
  dat_plt = weights_1$dat_plt,
  sa_var = NULL
)$table
```
**Summary statistics of the estimated balancing weights (exposures: \acr{edcs}; outcome: \acr{hitrtse}) (HELIX Study; 2013-2016).**
:::

::: {#supptbl-weights-2}
```{r weights-2}
tidy_res_weighted_fits(
  dat_tbl = weights_2$dat_tbl,
  dat_plt = weights_2$dat_plt,
  sa_var = NULL
)$table
```
**Summary statistics of the estimated balancing weights (exposures: \acr{edcs}; outcomes: glucocorticosteroids) (HELIX Study; 2013-2016).**
:::

::: {#supptbl-weights-3}
```{r weights-3}
tidy_res_weighted_fits(
  dat_tbl = weights_3$dat_tbl,
  dat_plt = weights_3$dat_plt,
  sa_var = NULL
)$table
```
**Summary statistics of the estimated balancing weights (exposures: glucocorticosteroids; outcome: \acr{hitrtse}) (HELIX Study; 2013-2016).**
:::

@@

::: {#supptbl-weights-1sa}
```{r weights-1sa}
tidy_res_weighted_fits(
  dat_tbl = weights_1SA$dat_tbl,
  dat_plt = weights_1SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
**Summary statistics of the estimated balancing weights for effect modification (exposures: \acr{edcs}; outcome: \acr{hitrtse}; modifier: sex) (HELIX Study; 2013-2016).**
:::

::: {#supptbl-weights-2sa}
```{r weights-2sa}
tidy_res_weighted_fits(
  dat_tbl = weights_2SA$dat_tbl,
  dat_plt = weights_2SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
**Summary statistics of the estimated balancing weights for effect modification (exposures: \acr{edcs}; outcomes: glucocorticosteroids; modifier: sex) (HELIX Study; 2013-2016).**
:::

::: {#supptbl-weights-3sa}
```{r weights-3sa}
tidy_res_weighted_fits(
  dat_tbl = weights_3SA$dat_tbl,
  dat_plt = weights_3SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
**Summary statistics of the estimated balancing weights for effect modification (exposures: glucocorticosteroids; outcome: \acr{hitrtse}; modifier: sex) (HELIX Study; 2013-2016).**
:::

@@

viz_desc_vars(
  dat = load_dat_request()$dat,
  vars = vars_of_interest(append_to_chem = "cdesc")$chemicals,
  fct_levels = c(1, 2, 3, 4),
  is_chem = TRUE
)$plot
```
**Measurement classification of \acr{edcs}, by cohort (HELIX Study; 2013-2016).** 
Coding: 1, quantifiable; 2, <LOD; 3, interference or out of range; 4. not analysed.
:::

@@

viz_desc_vars(
  dat = myphd::extract_cohort(load_steroids()$desc,
                              id_var = id_var,
                              st = 1, en = 3) |>
    tidylog::mutate(
      cohort = dplyr::case_when(
        cohort == "EDE" ~ "EDEN",
        cohort == "KAN" ~ "KANC",
        cohort == "MOB" ~ "MOBA",
        cohort == "RHE" ~ "RHEA",
        .default = cohort
      )
    ),
  vars = vars_of_interest(append_to_chem = NULL)$metabolites |>
    paste0("_cdesc"),
  fct_levels = c(1, 2, 3, 4),
  is_chem = FALSE
)$plot
```
**Measurement classification of the glucocorticosteroids, by cohort (HELIX Study; 2013-2016).** 
Coding: 1, quantifiable; 2, <LOQ; 3, interference or out of range; 4, not detected.
:::

### 2024-01-02 output/paper/_tables.qmd
First round of modifications for tables and figures done.

```{r pop-desc}
#| label: tbl-pop-desc
#| tbl-cap: Participant characteristics, by cohort and overall (HELIX Study; 2013-2016).

targets::tar_load("table1", store = store)
table1
```

@@

```{r edc-desc}
#| label: tbl-edc-desc
#| tbl-cap: Participants endocrine disruptors concentrations, by cohort and overall (HELIX Study; 2013-2016).

targets::tar_load("desc_chems_mets", store = store)
desc_chems_mets$desc_chems
```

@@

```{r met-desc}
#| label: tbl-met-desc
#| tbl-cap: Participants glucocorticosteroids concentrations, by cohort and overall (HELIX Study; 2013-2016).

desc_chems_mets$desc_mets
```

@@

```{r hypothesis-1}
#| label: tbl-hypothesis-1
#| tbl-cap: Pairwise differences between sex-specific marginal contrasts for the effect of \acr{edcs} on \acr{hitrtse} (HELIX Study; 2013-2016).

tidy_res_meffects(
  df = marginal_hypothesis_1SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```

```{r hypothesis-2}
#| label: tbl-hypothesis-2
#| tbl-cap: Pairwise differences between sex-specific marginal contrasts for the effect of \acr{edcs} on the glucocorticosteroids (HELIX Study; 2013-2016).

tidy_res_meffects(
  df = marginal_hypothesis_2SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```

```{r hypothesis-3}
#| label: tbl-hypothesis-3
#| tbl-cap: Pairwise differences between sex-specific marginal contrasts for the effect of the glucocorticosteroids on \acr{hitrtse} (HELIX Study; 2013-2016).

tidy_res_meffects(
  df = marginal_hypothesis_3SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```

>>>>

::: {#tbl-pop-desc}
```{r pop-desc}
targets::tar_load("table1", store = store)
table1
```
**Participant characteristics, by cohort and overall (HELIX Study; 2013-2016).**
:::

@@

::: {#tbl-edc-desc}
```{r edc-desc}
targets::tar_load("desc_chems_mets", store = store)
desc_chems_mets$desc_chems
```
**Participants endocrine disruptors concentrations, by cohort and overall (HELIX Study; 2013-2016).**
:::

@@

::: {#tbl-met-desc}
```{r met-desc}
desc_chems_mets$desc_mets
```
**Participants glucocorticosteroids concentrations, by cohort and overall (HELIX Study; 2013-2016).**
:::

@@

::: {#tbl-hypothesis-1}
```{r hypothesis-1}
tidy_res_meffects(
  df = marginal_hypothesis_1SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```
**Pairwise differences between sex-specific marginal contrasts for the effect of \acr{edcs} on \acr{hitrtse} (HELIX Study; 2013-2016).**
:::

::: {#tbl-hypothesis-2}
```{r hypothesis-2}
tidy_res_meffects(
  df = marginal_hypothesis_2SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```
**Pairwise differences between sex-specific marginal contrasts for the effect of \acr{edcs} on the glucocorticosteroids (HELIX Study; 2013-2016).**
:::

::: {#tbl-hypothesis-3}
```{r hypothesis-3}
tidy_res_meffects(
  df = marginal_hypothesis_3SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```
**Pairwise differences between sex-specific marginal contrasts for the effect of the glucocorticosteroids on \acr{hitrtse} (HELIX Study; 2013-2016).**
:::

### 2024-01-02 output/paper/manuscript.qmd
First round of modifications for tables and figures done.

```{r}
info_steroids <- readODS::read_ods("docs/steroids.ods")
print_tidy_abbreviations_steroids <- function(df, score) {
  cortisol_prod <- c(
    "20aDHF", "20bDHF", "5bDHF", "5aTHF", "5bTHF",
    "6OHF",
    "5a20acortol", "5a20bcortol", "5b20acortol", "5b20bcortol"
  )
  cortisone_prod <- c(
    "20aDHE", "20bDHE", "5aTHE", "5bTHE",
    "6OHE",
    "5b20acortolone", "5b20bcortolone"
  )
  corticosterone_prod <- c(
    "5aTHB", "5bTHB", "A", "17-DO-cortolone"
  )
  tmp <- df |>
    dplyr::filter(dplyr::case_when(
      score == "cortisol_prod" ~ acronym %in% cortisol_prod,
      score == "cortisone_prod" ~ acronym %in% cortisone_prod,
      score == "corticosterone_prod" ~ acronym %in% corticosterone_prod,
    )) |>
    dplyr::select(analyte, acronym) |>
    dplyr::arrange(analyte) |>
    dplyr::mutate(
      ret = glue::glue("{analyte} ({acronym})")
    )
  tmp$ret |>
    paste0(collapse = ", ")
}
```

@@

<!-- {{< include _figures.qmd >}} -->

>>>>

```{r}
info_steroids <- readODS::read_ods("../../docs/steroids.ods")
print_tidy_abbreviations_steroids <- function(df, score) {
  cortisol_prod <- c(
    "20aDHF", "20bDHF", "5bDHF", "5aTHF", "5bTHF",
    "6OHF",
    "5a20acortol", "5a20bcortol", "5b20acortol", "5b20bcortol"
  )
  cortisone_prod <- c(
    "20aDHE", "20bDHE", "5aTHE", "5bTHE",
    "6OHE",
    "5b20acortolone", "5b20bcortolone"
  )
  corticosterone_prod <- c(
    "5aTHB", "5bTHB", "A", "17-DO-cortolone"
  )
  tmp <- df |>
    dplyr::filter(dplyr::case_when(
      score == "cortisol_prod" ~ acronym %in% cortisol_prod,
      score == "cortisone_prod" ~ acronym %in% cortisone_prod,
      score == "corticosterone_prod" ~ acronym %in% corticosterone_prod,
    )) |>
    dplyr::select(analyte, acronym) |>
    dplyr::arrange(analyte) |>
    dplyr::mutate(
      ret = glue::glue("{analyte} ({acronym})")
    )
  tmp$ret |>
    paste0(collapse = ", ")
}
```

@@

{{< include _figures.qmd >}}
